---
title: "Final Project"
subtitle: "Data Science for Biologists, Spring 2021"
author: Umu Barry
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
# DON'T CHANGE THE NEXT LINE, except to add NEW options if you have any.
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo = TRUE, include = TRUE)

# Load all libraries you use HERE:
library(tidyverse)
```

<br><br>

## Introduction

```{r read-examine-data}
friends_emotions <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-08/friends_emotions.csv')

```

<br><br>

## Question 1

###During season 1 episode 3 of the friends show, what emotion (Joyful, Neutral, Mad) was more expressed?

### Methods

```{r question1_methods}
glimpse(friends_emotions) #glimpsing at the friends emotions data

friends_emotions %>% #ringing in friends emotions data
filter(season==1,episode==3, emotion %in% c("Joyful","Neutral","Mad"))%>% #filtering the season and episode I'm looking at, while also selecting three emotions
select(season, episode, emotion)-> Q1 #selecting the necessary needed data
Q1%>% #ringing in my renamed selection
  ggplot()+ #ringing in ggplot
aes(x= emotion, y= episode)+ #assigning X and Y axes
geom_col()+ #creating the graph 
theme_classic()+ #changing the theme/background of the graph 
labs(x= "Emotions", y="Episodes", title = "Q1 Plot", width=4,height=6) #naming X and Y axes, adding a title and the height and width. 

```


### Answer

Based on the graph, the emotion that was expressed the most was Neutral. 


<br><br>

## Question 2

### Between season 1 and 2 of friends, which season showed more Joyful emotions?

### Methods

```{r question2_methods}
glimpse(friends_emotions) #glimpsing at the friends emotions data
friends_emotions %>%  #ringing in friends emotions data
filter(season== "1", episode%in% c("1","2"),emotion=="Joyful")%>% #filtering the needed emotion which i
select(season,episode,emotion)%>%##selecting the necessary needed data
group_by(episode)%>%
mutate(season = if_else(episode =="1","1","2"))%>%
ggplot()+
aes(x=season, y= emotion)+
geom_col()+
theme_classic()
labs(x="Season",y ="Emotion", title= "Q2 Plot", width=5, height=7)
```

### Answer
Based on the plot, Season 2 showed more joyful emotions.


<br><br>

## Question 3

#### During season 3 episode 6 of the friends show, what emotion (sad and scared) was least expressed

### Methods

```{r question3_methods}
glimpse(friends_emotions)
friends_emotions %>% #ringing in friends emotions data
filter(season==3,episode==6, emotion %in% c("Scared","Sad"))%>% #filtering the season and episode I'm looking at, while also selecting three emotions
select(season, episode, emotion)-> Q3 #selecting the necessary needed data
Q3%>% #ringing in my renamed selection
  ggplot()+ #ringing in ggplot
aes(x= emotion, y= episode)+ #assigning X and Y axes
geom_col()+ #creating the graph 
theme_classic()+ #changing the theme/background of the graph 
labs(x= "Emotions", y="Episodes", title = "Q1 Plot", width=4,height=6) #naming X and Y axes, adding a title and the height and width. 

```

### Answer

Acoording to the plot, least here


<br><br>

## Question 4

#### Out of all the seasons and epidose of friends which emotion was the most expressed?

### Methods

```{r question4_methods}
glimpse(friends_emotions)
friends_emotions%>%
  ggplot()+ #ringing in ggplot
aes(x=emotion)+ #assigning X and Y axes
geom_bar()+ #creating the graph 
theme_classic()+ #changing the theme/background of the graph 
labs(x= "Emotions", y="Episodes", title = "Q1 Plot", width=4,height=6) #naming X and Y axes, adding a title and the height and width. 


```

### Answer

Neutral
